### 2015-02-06 fundamentals/examples.tex
reword big paragraph

    \item \textbf{Reactor} (\Class{cycamore::Reactor}): This is a reactor
        model that requests any number of input fuel types and transmutes them
        to static compositions when they are burnt and discharged from the
        core.  . The reactor was configured to model a light water reactor
        with a 3 batch core (20,000 kg HM per batch) operating on an 18 month
        cycle with a 2 month refuel time.  The reactor was also configured to
        take in either enriched UOX fuel or recycled MOX fuel - preferring the
        latter if available.

@@

For the once through case, the \Class{Reactor} was set to offer all spent fuel
as waste.  For the 1-pass recycle case, the \Class{Reactor} offered spent UOX
into a spent fuel market where it is preferentially sent to separations, but
spent MOX is still offered as waste.  In the infinite-pass recycle case, the
\Class{Reactor} offers all spent fuel into a spent fuel market. Because the
separations facility requests spent fuel with a higher preference than the
repository, it is sent there if possible.  All these preferences are easy to
adjust and \Cyclus will dynamically handle supply constraints and non-uniform
preference resolution.  It is notable that separations and recycle fuel
fabrication capacity is deployed identically in all simulations.  In the
once-through case, the recycling loop never acquires material, and so reactors
always receive fresh UOX fuel.  In the 1-pass recycle case, the recycle loop
only acquires spent UOX.  The \gls{DRE} ensures everything operates smoothly
in all cases.

Cyclus' discrete materials make single-pass recycle easy to implement.  The
reactors keep track of fuel as discrete batches. A reactor remembers where it
received each batch from.  If a batch was received from the recycled fuel
fabrication facility, it does not offer it to separations and instead sends it
to the repository directly.  The material flows for the 1-pass recycle case are
shown in Figure \ref{fig:flowmodopen}.

@@

This results in the material flows in Figure \ref{fig:flowclosed}.  A
similarly trivial change was used to switch from the once through to a 1-pass
fuel cycle.  Note that the \Class{Reactor} always transmutes fuel into fixed
compositions, the error in isotopic compositions is larger in the
infinite-pass recycle case.

>>>>

    \item \textbf{Reactor} (\Class{cycamore::Reactor}): This is a reactor
        model that requests any number of input fuel types and transmutes them
        to static compositions when they are burnt and discharged from the
        core.  . The reactor was configured to model a light water reactor
        with a 3 batch core (20,000 kg HM per batch) operating on an 18 month
        cycle with a 2 month refuel time.  The reactor was also configured to
        take in either enriched UOX fuel or recycled MOX fuel.

@@

Modifying the input file specification to model each of the 3 fuel cycles was
done by making simple adjustments to the commodities and trade preferences for
each of the facilities.  The reactor was configured to request recycled MOX
fuel with a higher preference then new UOX fuel. For the once through case,
the \Class{Reactor} was set to offer all spent fuel as waste.  For the 1-pass
recycle case, the \Class{Reactor} offered spent UOX into a spent fuel market,
but spent MOX is still offered as waste.  In the infinite-pass recycle case,
the \Class{Reactor} offers all burned fuel into a spent fuel market. The
separations facility requests spent fuel with a higher preference than the
repository resulting in preferential recycle.  All these preferences are easy
to adjust and \Cyclus dynamically handles supply constraints and non-uniform
preference resolution.  It is notable that separations and recycle fuel
fabrication capacity are deployed identically in all simulations.  In the once
through case, the recycling loop never acquires material, and so reactors
always receive fresh UOX fuel.  The \gls{DRE} ensures everything operates
smoothly in all cases.

Cyclus' discrete materials make single-pass recycle easy to implement.  The
reactors keep track of fuel as discrete batches. A reactor remembers where it
received each batch from.  If a batch was received from the recycled fuel
fabrication facility, it does not offer it to separations and instead offers
it as a waste commodity which is only requested by the repository.  The
material flows for the 1-pass recycle case are shown in Figure
\ref{fig:flowmodopen}.

@@

This results in the material flows in Figure \ref{fig:flowclosed}.  A
similarly trivial change was used to switch from the once through to a 1-pass
fuel cycle.  Note that because the reactors always transmute fuel into fixed
compositions, the error in isotopic compositions is larger for the
infinite-pass recycle case.
